\documentclass[12pt]{article}

%packages
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{mathdots}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{hyperref}
%Margins etc...
\setlength{\textheight}{240mm}
\setlength{\topmargin}{-17mm} \setlength{\oddsidemargin}{-4mm}
\setlength{\textwidth}{166mm} \setlength{\parindent}{0mm}
\setlength{\marginparsep}{9mm} \setlength{\parskip}{3mm}
\pagestyle{empty}

\begin{document}
\begin{center}
\huge{MAT013 - R: Chapter 4 Lab Sheet}\\
\begin{center}
\tiny{(This sheet was last updated on \today)}
\end{center}
\end{center}

\begin{enumerate}
\item Create a (single) data set containing the name of the observations from ``JJJ'' and ``MMM'' as well as a new variable which is ``Y'' if the individual is clinically obese and ``N'' otherwise.
\item Create a (single) data set containing the total number of birthday candles used throughout the lives of every individual from both ``JJJ'' and ``MMM''.
\item Obtain the first even numbers less than 240.
\item Create a function that outputs a scatter plot of height against weight for observations in the ``JJJ''  and ``MMM'' data sets. Modify the function so that it outputs the plot to a pdf file.
\item Create a function that computes the left over life savings after a given quantity of spending on a given quantiy of shopping trips from the ``JJJ'' data set.
\item Modify the above function so that a default value is given to spend of 430 and a default value of 3 trips.
\item Modify the above function so that a message is printed if the spend is 0 and no other output is given.
\item Create a function that creates 15 data sets each with updated savings in pounds for observations in the ``JJJ'' and ``MMM'' data sets for varying values for the number of trips (1 to 15).
\item Download the files \href{https://docs.google.com/file/d/0Bx_zrw5uAafbc3B1WndVdk1FM1E/edit}{``File\_1.csv - File\_200.csv''} and create a function that automatically imports them.
\item Include the above code in a script file that could be run using the ``source'' command and re run whenever the above data sets get updated.
\end{enumerate}




\end{document}
