\documentclass[12pt]{article}

%packages
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{mathdots}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{hyperref}
%Margins etc...
\setlength{\textheight}{240mm}
\setlength{\topmargin}{-17mm} \setlength{\oddsidemargin}{-4mm}
\setlength{\textwidth}{166mm} \setlength{\parindent}{0mm}
\setlength{\marginparsep}{9mm} \setlength{\parskip}{3mm}
\pagestyle{empty}

\begin{document}
\begin{center}
\huge{MAT013 - R: Chapter 5 Lab Sheet}\\
\begin{center}
\tiny{(This sheet was last updated on \today)}
\end{center}
\end{center}

\begin{enumerate}
\item Using sql, create a copy of the MMM and JJJ data sets, including all the variables.
\item Using sql, create the previous copies selecting just the variables, Name, Age, Sex, Random\_Number, as well as the bmi of the observations.
\item For the following data set:
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Var1&Var2&Var3&Var4&Var5\\\hline\hline
A&1&A&2&B\\\hline
A&1&A&2&B\\\hline
B&1&A&1&C\\\hline
C&2&B&2&D\\\hline
C&2&C&1&E\\\hline
\end{tabular}
\end{center}
\begin{enumerate}
\item Create a copy of the data set removing complete duplicate rows.
\item Create a copy of the data set removing duplicates of Var2.
\item Create a copy of the data set removing duplicates of Var3 and Var4.
\item Create a copy of the data set selecting only observations where Var2$>$Var4.
\item Create a copy of the data set ordering by Var1.
\item Create a data set containing the mean, std, max, min and variance of Var4 and Var2 by Var1.
\end{enumerate}
\item Download the data sets \href{https://docs.google.com/file/d/0Bx_zrw5uAafbekVHY0tLMlJydzA/edit}{ ``dogs.csv}'' and \href{https://docs.google.com/file/d/0Bx_zrw5uAafbVzNLeVNDSXNiSkU/edit}{``cats.csv''} use sql to:
\begin{enumerate}
\item create an inner join.
\item a left outer join.
\item a right outer join (you won't be able to use sql for this in R).
\item a full outer join (you won't be able to use sql for this in R).
\end{enumerate}
\item Create a histogram for the Height of people in the JJJ data set.
\item Modify the above plot to be a density plot with your own legends labels and title.
\item Obtain a scatter plot of weight against height for people in the JJJ data set.
\item Modify the above plot so that the points are proportional to the age.
\item Obtain a box plot for the Height of people in the JJJ data set by sex.
\item Obtain a scatter plot of Weight against Height with a smoothed trend line.
\item Obtain histograms of height against weight, compartmentalised by sex.
\item Create a scatter plot with a fitted linear model for Height against Weight for all people in MMM and JJJ. Compartmentalise your graphs based on the data set and the sex.
\item Save the above graph to file.
\item Get all of todays trends on twitter.
\item Search for all tweets with the ``orms" hashtag.
\item Find the tweets from INFORMS.
\end{enumerate}






\end{document}
