\documentclass[12pt]{article}

%packages
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{mathdots}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{hyperref}
%Margins etc...
\setlength{\textheight}{240mm}
\setlength{\topmargin}{-17mm} \setlength{\oddsidemargin}{-4mm}
\setlength{\textwidth}{166mm} \setlength{\parindent}{0mm}
\setlength{\marginparsep}{9mm} \setlength{\parskip}{3mm}
\pagestyle{empty}

\begin{document}
\begin{center}
\huge{MAT013 - SAS: Chapter 5 Lab Sheet}\\
\begin{center}
\tiny{(This sheet was last updated on \today)}
\end{center}
\end{center}

\begin{enumerate}
\item Re-produce the SAS code from the notes:
\begin{enumerate}
\item Using proc sql, create a copy of the mat008.mmm and mat008.jjj data sets, including all the variables.
\item Using proc sql, create the previous copies selecting just the variables, Name, Age, Sex, random number, as well as the bmi of the observations.
\item For the following data set:
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Var1&Var2&Var3&Var4&Var5\\\hline\hline
A&1&A&2&B\\\hline
A&1&A&2&B\\\hline
B&1&A&1&C\\\hline
C&2&B&2&D\\\hline
C&2&C&1&E\\\hline
\end{tabular}
\end{center}
\begin{enumerate}
\item Create a copy of the data set removing complete duplicate rows.
\item Create a copy of the data set removing duplicates of Var2.
\item Create a copy of the data set removing duplicates of Var3 and Var4.
\item Create a copy of the data set selecting only observations where Var2$>$Var4.
\item Create a copy of the data set ordering by Var1.
\item Create a data set containing the mean, std, max, min and variance of Var4 and Var2 by Var1.
\end{enumerate}
\item Download the data sets \href{http://db.tt/uYy2jxrc}{ ``dogs.csv}'' and \href{http://db.tt/8UP3VUwg}{``cats''} use proc sql to:
\begin{enumerate}
\item create an inner join.
\item a left outer join.
\item a right outer join.
\item a full outer join.
\end{enumerate}
\item Create a new function entitled ``Gsum" and compute the geometric sum $\sum_{k=0}^ni^k$ for the following data set:
\begin{center}
\begin{tabular}{|c|c|}
\hline
n&i\\\hline\hline
1&1\\\hline
2&1\\\hline
3&2\\\hline
4&2\\\hline
5&2\\\hline
6&2\\
\hline
\end{tabular}
\end{center}
\item Minimise the function $x^2-x-2y-xy+y^2$.
\item Minimise the above function for $x\leq 0$ and $y\geq 2$.
\item Solve the following optimisation problem:
\begin{center}
Maximise: $f(x_1,x_2,x_3)=x_1+x_2+x_3$ subject to:
\end{center}
\begin{align}
x_1,x_2,x_3\geq0\\
3x_1+2x_2-x_3\leq& 1\\
-2x_1-3x_2+2x_3\leq&1
\end{align}
\end{enumerate}
\end{enumerate}
\end{document}
